Analysis of Patient Derived Xenograft Growth Curves

### 2022-04-21 paper_Kuhlers.Rmd
paper updates

Tumor volume data was obtained from the PDXnet Portal,
queried for all colon adenocarcinoma.

>>>>

Mice were randomized to treatment groups and did not begin observation
until reaching a tumor volume of 150-200mm^3 (Evrard et al).

### Data Processing

Tumor volume data was obtained from the PDXnet Portal,
queried for all available colon adenocarcinoma.
Observation days were rescaled to the number of days the sample
was observed, so that the time origin was 0 for all samples.
For example, if the mouse was staged on observation day 30,
this became day 0, and all subsequent measurements on this mouse were scaled to
days since day 30. Days were then rescaled to months.

### Mixed Effects Model

Tumor volumes were analyzed using generalized linear mixed effects models.
Fixed effects included were time and the time-drug interaction.
The drug main effect was not included to model equal mean weight
at baseline amongst all treatment groups.
